---
title: "untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Women Inventors

The raw data is in rawgender. The post inventor disambiguated data is in 

1. Load the inventor table 
2. Filter on the male_flag (why is it called that really)
3. Use the patent_inventor cross walk table to make the join across to granted patents
4. From there do other things.

Read the methods paper on gender at this link [https://s3.amazonaws.com/data.patentsview.org/documents/On-line+Appendix+-+Gender+Attribution+of+USPTO+Inventors.pdf](https://s3.amazonaws.com/data.patentsview.org/documents/On-line+Appendix+-+Gender+Attribution+of+USPTO+Inventors.pdf). Lots of interesting content including a WIPO list.

```{r}
women_inventors <- inventor %>% filter(male_flag == 0)

save(women_inventors, file = "data/women_inventors.rda", compress = "xz")
```


Make the link to the patents table through the patents_inventor table

```{r}
women_patents <- patent_inventor %>% 
  mutate(women = .$inventor_id %in% women_inventors$id) %>% 
  filter(women == TRUE)

save(women_patents, file = "data/women_patents.rda", compress = "xz")
```

```{r}
women_granted <- patent %>% 
  mutate(women = .$id %in% women_patents$patent_id) %>% 
  filter(women == TRUE)
```

test if more than one woman is present on the same patent. Expecting 1.7 million and got 1.3 million. Answer is yes. 

```{r}
women_patents %>% 
  count(patent_id, sort = TRUE) %>% 
  nrow() # matches the number of patent docs returned above.
```

```{r}
women_ipc <- ipc %>% 
  mutate(women = .$patent_id %in% women_patents$patent_id) %>% 
  filter(women == TRUE) %>% 
  unite(ipc_subclass, c("section", "ipc_class", "subclass"), sep = "", remove = FALSE) %>% 
  unite(ipc_maingroup, c("ipc_subclass", "main_group"), sep = "/", remove = FALSE)

women_ipc %>% 
  count(ipc_subclass, sort = TRUE) %>% 
  View()

women_ipc %>% 
  count(ipc_maingroup, sort = TRUE) %>% 
  View()

save(women_ipc, file = "data/women_ipc.rda", compress = "xz")
```

